Towards Correct Legion

### 2017-08-26 correctnesshpc/paper.tex
draft of progress and preservation theorems

TODO: Noah, if you want to put any other proof stuff here feel free.

>>>>

\subsection{Full Implementation of the Specification}
In addition to proving theorems and lemmas about the semantics of Legion as they
relate to HPC memory models, another goal of a formal specification is to ensure
both the completeness and soundness of the Core Legion model. Much of the
necessary implementation work here is ensuring that the entire grammar of the
language is both type safe and its operational semantics contain transition
rules for all productions in the language.

To do this we are writing our proofs of progress and preservation (ie. that well
typed expressions evaluate to a value or diverge and that
every transition in the operational semantics produces a well typed value given
a well typed expression) together with our implementation of the semantics of
the Core Legion language.

Thus far this approach has acted as a sanity check for our implementation and helped us
handle unspecified corner cases in the Core Legion specification (eg. the list
of functions in the \texttt{T-Program} relation has no corresponding transition in the
operational semantics).

The theorems we are using are described in Figure~\ref{preservationtheorem} and
Figure~\ref{progresstheorem} (see
\texttt{https://github.com/lanl/formallegion} for the in progress proofs).

\begin{figure}
\begin{BVerbatim}
Theorem preservation : forall (e5:e) (t:T) (E:E) (M:M) (L:L) 
(H:H) (S:list (e * e)) (C:list e) (T:T),
    exists v,
      eval M L H S C e5 v E ->
      typing EmptyContext EmptyPriv EmptyConstraint e5 T  ->
      exists G P Omega T, typing G P Omega v T.
\end{BVerbatim}
\caption{preservation theorem}
\label{preservationtheorem}
\end{figure}

\begin{figure}
\begin{BVerbatim}
Theorem progress : forall  (e5:e) (t:T) (M:M) (H:H)  
(C:list e) (T1 T2:T) L (S:list (e * e)),
    typing EmptyContext EmptyPriv EmptyConstraint e5 T1  ->
    (exists E v ,
        is_value v ->
        eval M L H S C e5 v E).
\end{BVerbatim}
\caption{progress theorem}
\label{progresstheorem}
\end{figure}
